### 2023-01-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b4bd3f5d37331adac55f411fca44a592ffee5897 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@4492ba2cf17e43e9026bc17d4063ad707480e746 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b87502c61ca9e00e7fbeba50799359bb66a76753 🚀

There is also an analytic way to approximate this distribution using the
normal approximation to binomial. As a reminder, as the total number of
samples \(N\) from a binomial distribution for \(n\) trials with success
probability \(p\) from approaches infinity, the sum of total successes
across all samples approaches a normal distribution with mean \(np\) and
variance \(np(1-p)\). We can use this to correct the estimate \(p_{ij}\)
based on the expected false-negative-rate \(p_{fn}\) and false-positive
rate \(p_{fp}\) to obtain the limiting distribution as the number of
resamples approaches infinity for the resampled \(p_{ij}^*\) for a given
number of particles \(n_p\). We do this by first adjusting for the rates
of observation error to get the mean resampled probability,
\(\mathbb{E}[{p_{ij}^*}]\), as

@@

which is obatinable by definition (supp 1.)

For notation, here we refer to a normal distribution with mean \(\mu\)
and standard-deviation \(\sigma\) as \(\mathcal{N}(\mu,\sigma)\)

Then yields the normal approximation

>>>>

There is also an analytic way to approximate this distribution using the
normal approximation to binomial. As a reminder, as the total number of
samples \(N\) from a binomial distribution for \(n\) trials with success
probability \(p\) from approaches infinity, the sum of total successes
across all samples approaches a normal distribution with mean \(np\) and
variance \(np(1-p)\). For notation, here we refer to a normal
distribution with mean \(\mu\) and standard-deviation \(\sigma\) as
\(\mathcal{N}(\mu,\sigma)\). We can use this to correct the estimate
\(p_{ij}\) based on the expected false-negative-rate \(p_{fn}\) and
false-positive rate \(p_{fp}\) to obtain the limiting distribution as
the number of resamples approaches infinity for the resampled
\(p_{ij}^*\) for a given number of particles \(n_p\). We do this by
first adjusting for the rates of observation error to get the mean
resampled probability, \(\mathbb{E}[{p_{ij}^*}]\), as

@@

This yields the normal approximation
